---
title: "Mohamad Bazzi's CV"
author: Mohamad Bazzi
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
    dev: png
knit: pagedown::chrome_print
---

```{r, include=FALSE}
knitr::opts_chunk$set(results='asis', dpi = 36, dev = "png",
                      dev.args = list(pdf = list(colormodel = 'rgb', useDingats = TRUE),
                                      tiff = list(compression = 'lzw')),echo = FALSE)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
# For this to work update line 32 in the cv_printing_functions file and then grant access via Google docs.
CV <- create_CV_object(
   data_location = "https://docs.google.com/spreadsheets/d/1Cxvtix6rJM7hueacSwQl5cxpd26Eh2-4MBzBWSJhqNM/edit?usp=sharing",
   pdf_mode = params$pdf_mode)
```

```{r}
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```

# Aside

## Contact {#contact}

-   <i class="fa fa-envelope"></i> [bazzi\@stanford.edu](mailto:bazzi@stanford.edu){.email}
-   <i class="fa fa-phone"></i> +46 738508592
-   <i class="fa fa-phone"></i> +1 650 698 7962
-   <i class="fa fa-github"></i> [Github](https://github.com/mohabazzi)
-   <i class="fab fa-researchgate"></i> [Researchgate](https://www.researchgate.net/profile/Mohamad-Bazzi-2)
-   <i class="fa fa-linkedin" aria-hidden="true"></i> [Linkedin](https://www.linkedin.com/in/mohammed-bazzi-71543580)

## Programming & Software Skills {#skills}

```{r}
CV %>% print_skill_bars()
```

# Main

## Mohamad Bazzi {#title}

### Evolutionary Biologist (Ph.D)

```{r}
CV %<>% print_text_block("intro") 
```

## Education {data-icon="graduation-cap" data-concise="true"}

```{r}
CV %<>% print_section('education')
```

## Research Experience {data-icon="laptop"}

```{r}
CV %<>% print_section('research_positions')
```

::: aside
```{r}
CV %<>% print_text_block('research_experience_aside')
```
:::

## Industry Experience {data-icon="suitcase"}

```{r}
CV %<>% print_section('industry_positions')
```

## Teaching Experience {data-icon="chalkboard" data-concise="true"}

```{r}
CV %<>% print_section('teaching_positions')
```

## Leadership Experience {data-icon="chalkboard-teacher"}

```{r}
CV %<>% print_section('leadership_history')
```

## Awards <i class="fa-regular fa-bookmark"></i>

```{r}
CV %<>% print_section('academic_history')
```

## Selected Press (About) {data-icon="newspaper"}

```{r}
CV %<>% print_section('about_me_press')
```

## Selected Press (By) {data-icon="newspaper"}

```{r}
CV %<>% print_section('by_me_press')
```

## Selected Publications {data-icon="book"}

```{r}
CV %<>% print_section('academic_articles')
```

## Peer Review Service

```{r}
CV %<>% print_section('peer_review_service')
```

## Invited Academic Talks

```{r}
CV %<>% print_section('invited_seminars')
```

## Synergistic Activity

```{r}
CV %<>% print_section('synergistic_activity')
```

## Field Experience {data-icon="gavel"}

```{r}
CV %<>% print_section('field_experience')
```

## Graphic Design {data-icon="pen-nib"}

### Software

-   CorelDraw
-   Adobe Photoshop & Illustrator

N/A

## Ancillary Courses & Certificates {data-icon="bookmark"}

```{r}
CV %<>% print_section('ancillary_courses')
```
